Reanalysis Step 2: Multiple Imputation

### 2025-08-29 reanalysis-2-multiple_imputation.qmd
run

@@

>>>>

# Debug: Check if any methods have invalid values
invalid_methods <- custom_methods[!custom_methods %in% c("", "pmm", "logreg", "polyreg", "polr", "norm", "norm.boot", "norm.nob", "norm.predict", "sample", "cart", "rf", "2l.norm", "2l.lmer", "2l.pan", "2lonly.mean", "2lonly.norm", "2lonly.pmm")]
if (length(invalid_methods) > 0) {
  log_message(paste0("WARNING: Invalid imputation methods detected: ", paste(names(invalid_methods), "=", invalid_methods, collapse=", ")))
  # Reset any invalid methods to appropriate defaults
  for (var in names(invalid_methods)) {
    if (var %in% names(custom_methods)) {
      # Set to empty string to skip imputation for now
      custom_methods[var] <- ""
      log_message(paste0("Reset method for ", var, " to '' (no imputation)"))
    }
  }
}

# Ensure methods vector has proper names
if (is.null(names(custom_methods))) {
  log_message("ERROR: custom_methods has no names. Setting names from df_mice columns.")
  names(custom_methods) <- colnames(df_mice)
}

# Print diagnostic info
log_message(paste0("Number of variables in custom_methods: ", length(custom_methods)))
log_message(paste0("First few method assignments: ", 
                  paste(head(names(custom_methods)), "=", head(custom_methods), collapse=", ")))

@@

# Final check on methods before running MICE
log_message("Final method check before imputation:")
methods_with_values <- custom_methods[custom_methods != ""]
log_message(paste0("Variables to be imputed: ", paste(names(methods_with_values), collapse=", ")))
log_message(paste0("Methods to be used: ", paste(unique(methods_with_values), collapse=", ")))
